### 2022-05-26 main/chapter_2ljets.tex
conclude draft of leptons section

\subsection{Trigger}
There would be no event variables if not for the trigger.
When living our daily lives, we are bombarded with sensory data and must pay
attention only only those gems few of any use, to avoid exhausting our
processing capacity.
Running \atlas\ is no different.

@@

\TODO{signal objects have isolation criteria}

\TODO{lepton pairs SF-OS for Z}

>>>>

\subsection{Trigger}
\label{sec:2ljets_trigger}
There would be no event variables if not for the trigger.
When living our daily lives, we are bombarded with sensory data and must pay
attention only only those gems few of any use, to avoid exhausting our
processing capacity.
Running \atlas\ is no different.

@@

Leptons in $\twoljets$ are further sliced into two classes:
`baseline' and `signal'.
Baseline leptons and are used in background estimation methods and to ensure
orthogonality with other \atlas\ analyses, which study events with differing
lepton counts.
Baseline requirements are softer and lower quality than signal requirements.

Any event used in regions of the $\twoljets$ electroweak analysis is required
to have exactly two baseline leptons and exactly two signal leptons, meaning
that the event has two reconstructed leptons which pass both sets of criteria.
This vetoes events with soft or low quality third leptons, ensuring that those
three-lepton events can be used independently in other studies.

Baseline leptons are required only to have  $\pt > 3~\eV[G]$ for muons and
$\pt > 4.5~\eV[G]$ for electrons.
Signal leptons are all required to have $\pt > 10~\eV[G]$, along with tighter
quality and isolation requirements, details of which can be found in the
paper~\cite{atlas2022searches}.

All leptons used in regions of the $\twoljets$ electroweak analysis are signal
leptons with $\pt > 25~\eV[G]$.
This harder requirement reduces backgrounds, moves our selections away from the
lowest trigger thresholds, and matches the precedent set by previous
work~\cite{atlas_23l_SUSY_2016_24}.
